\papertitle

### 2025-04-24 src/tex/ms.tex
[showyourwork] overleaf sync

However, in reality, computational scaling with the number of particles is not of great importance, as typical analyses would involve many small calculations of the centre of mass, such that constant computational overheads will dominate. 
To compare computational efficiencies, \cref{fig:comp_efficiency} presents the time taken for both algorithms with increasing number of iterations for a \num{20} particle systems.
The \emph{pseudo}-centre of mass recentering method is approximately twice as fast as the \textsc{geomstats} implementation of the intrinsic method, due to reduced complexity and number of steps. 
%
\begin{figure}
    \centering
    \includegraphics[width=8cm]{Fig6.pdf}
    \caption{Increasing number of calculations of the centre of mass of an example 20 particle system against computational time for both methods. 
    All calculations run on an Apple Macbook Pro with M3 chipset.}
    \label{fig:comp_efficiency}
    %\script{Fig6.py}
\end{figure}
%

>>>>

However, in reality, computational scaling with the number of particles is not of great importance, as typical analyses would involve many small calculations of the centre of mass, such that constant computational overheads will dominate. 
To compare computational efficiencies, \cref{fig:comp_efficiency} presents the time taken for both algorithms with increasing number of iterations for a \num{20} particle systems.
The \emph{pseudo}-centre of mass recentering method is more than twice as fast as the \textsc{geomstats} implementation of the intrinsic method, due to reduced complexity and number of steps. 
%
\begin{figure}
    \centering
    \includegraphics[width=8cm]{Fig6.pdf}
    \caption{Increasing number of calculations of the centre of mass of an example 20 particle system against computational time for both methods. 
    All calculations run on an Apple Macbook Pro with M3 chipset.}
    \label{fig:comp_efficiency}
    \script{Fig6.py}
\end{figure}
%
